---
title: "Innovalab-UPCH"
output: 
  flexdashboard::flex_dashboard:
    logo: https://user-images.githubusercontent.com/39299104/207467842-d92416da-c312-4a9c-9cbf-a23a93da6465.png
    favicon: https://raw.githubusercontent.com/healthinnovation/innovar/gh-pages/favicon.ico
    orientation: columns
    vertical_layout: fill
    navbar:
        - { icon: "fa-github", href: "https://github.com/healthinnovation", align: right}
    self_contained: false
    lib_dir: "lib"
---


<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto+Slab&display=swap');
body{
    font-family: 'Roboto Slab', serif;
}

.navbar{
    padding-left: 28px;
}

.navbar-logo {
    margin-top: 2px;
    width: 36.5px;
    position: fixed;
    left: 2px;
    margin-bottom: 2px;
}

.navbar-inverse {
    background-color: #070807;
    border-color: #070807;
}
.navbar-inverse .navbar-brand {
    color: #ffffff;
}
.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
    color: #ffffff;
    background-color: #ffffff2e;
}
.navbar-inverse .navbar-nav>li>a {
    color: #ffffff;
}
.navbar-inverse .navbar-brand:hover, .navbar-inverse .navbar-brand:focus {
    color: #ffffff;
    background-color: #ffffff00;
}
</style>


```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(DT)
library(crosstalk)
library(reactable)
library(htmltools)
library(plotly)
library(echarts4r)
```

```{r}
health_data <- read_csv("resources/Metadata-Health.csv")
socio_data <- read_csv("resources/Metadata-Sociodemo.csv")
climate_data <- read_csv("resources/Metadata-Climate.csv")
data_for_barplot <- data.frame(
  category = c("Health","Socioeconomic","Climate"),
  values = c(nrow(health_data),nrow(socio_data),nrow(climate_data))
  ) 
sd <- SharedData$new(data_for_barplot)
```

```{r}
dataset <- bind_rows(health_data, socio_data, climate_data, .id = "type") 
```

```{r}
dataset_type <- dataset %>% 
  group_by(type, Week) %>% 
  summarise(total = n()) %>% 
  complete(Week = unique(dataset$Week)) %>% 
  replace_na(list(total = 0)) %>% 
  ungroup() %>% 
  mutate(
    type = factor(
      type, levels = 1:n_distinct(dataset$type), 
      labels = c("Health", "Socioeconomic", "Climate")
    )
  )
```
```{r}
dataset_total <- dataset_type %>% 
  pivot_wider(id_cols = Week, names_from = type, values_from = total) %>% 
  mutate(Total = Health + Socioeconomic + Climate) %>% 
  pivot_longer(Health:Total, names_to = "type", values_to = "total") %>% 
  mutate(
    type = factor(type, levels = c("Health", "Socioeconomic", "Climate", "Total"))
  )
```


Main {data-icon="fa fa-bar-chart"}
=====================================================================


Column {data-width=650}
-----------------------------------------------------------------------

### Reviewed datasets by category

```{r}
p1 <- ggplot(data = sd, aes(x = category, y = values)) + 
  geom_bar(stat = "identity", color = "#374be6", fill = "#374be6") + 
  coord_flip() +
  theme_minimal() + 
  labs(x = "", y = "", title = "Systems mapped")

p1 %>% 
  ggplotly() %>% 
  config(displayModeBar = F)
```

### Reviewed datasets by category and week
```{r}
p2 <- dataset_total %>% 
  ggplot(aes(x = Week, y = total, color = type))+
  geom_line(alpha = 0.6) +
  geom_point(alpha = 0.6) +
  ggsci::scale_color_npg() +
  theme_minimal() +
  labs(x = "Week", y = "N° of reviewed datasets", color = "Category")

p2 %>%
  ggplotly() %>%
  config(displayModeBar = F)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Graph

```{r}
health_data_0 <- read_csv("resources/Metadata-Health_0.csv")
socio_data_0 <- read_csv("resources/Metadata-Sociodemo_0.csv")
climate_data_0 <- read_csv("resources/Metadata-Climate_0.csv")
totalfornet <- bind_rows(health_data_0,socio_data_0,climate_data_0)
```

```{r}
size_value_v1 <- totalfornet %>% 
  group_by(Institution) %>% 
  summarise(totalfornet = n())
```

```{r}
size_value_v2 <- totalfornet %>% 
  rename(data_system = `Data system`) %>% 
  group_by(Institution,data_system) %>% 
  summarise(totalfornet = n()) %>% 
  filter(!data_system %in% c("MINSA", "INEI","MINAM","MIDAGRI"))
```

```{r}
nodes <- data.frame(
  name = c(as.vector(unique(totalfornet$Institution)),as.vector(unique(totalfornet$`Data system`))),
  value = c(size_value_v1$totalfornet*3,size_value_v2$totalfornet*4),
  size = c(size_value_v1$totalfornet*3,size_value_v2$totalfornet*4),
  grp = c("MINSA", "INEI","MINAM","MIDAGRI",
          "MINSA","MINSA",rep("INEI",9),"MINAM",
          "MIDAGRI","MIDAGRI"),
  stringsAsFactors = FALSE
  )
```

```{r}
inei <- totalfornet %>% 
  rename(data_system = `Data system`) %>% 
  group_by(Institution,data_system) %>% 
  summarise(totalfornet = n())%>% 
  filter(Institution == "INEI") %>% 
  ungroup(Institution) %>% 
  select(data_system) %>%
  pull()
```

```{r}
minam <- totalfornet %>% 
  rename(data_system = `Data system`) %>% 
  group_by(Institution,data_system) %>% 
  summarise(totalfornet = n())%>% 
  filter(Institution == "MINAM") %>% 
  ungroup(Institution) %>% 
  select(data_system) %>%
  pull()
```

```{r}
midagri <- totalfornet %>% 
  rename(data_system = `Data system`) %>% 
  group_by(Institution,data_system) %>% 
  summarise(totalfornet = n())%>% 
  filter(Institution == "MIDAGRI") %>% 
  ungroup(Institution) %>% 
  select(data_system) %>%
  pull()
```

```{r}
minsa <- totalfornet %>% 
  rename(data_system = `Data system`) %>% 
  group_by(Institution,data_system) %>% 
  summarise(totalfornet = n())%>% 
  filter(Institution == "MINSA") %>% 
  ungroup(Institution) %>% 
  select(data_system) %>%
  pull()
```

```{r}
edges <- data.frame(
  source = c(
    rep("INEI",9),
    "MINAM",
    rep("MIDAGRI",2),
    rep("MINSA",2)
    ),
  target = c(inei,minam,midagri,minsa)
  )
```

```{r}
e_charts() |> 
  e_graph() |> 
  e_graph_nodes(nodes, name, value, size,grp) |> 
  e_graph_edges(edges, source, target)
```


Health {data-icon="fa fa-database"}
===============================================================

```{r}
reactable(health_data_0, highlight = TRUE)
```

Socioeconomic {data-icon="fa fa-database"}
===============================================================

```{r}
reactable(socio_data_0, highlight = TRUE)
```


Climate {data-icon="fa fa-database"}
===============================================================

```{r}
reactable(climate_data_0, highlight = TRUE)
```
