---
title: "Innovalab-UPCH"
output: 
  flexdashboard::flex_dashboard:
    logo: https://user-images.githubusercontent.com/39299104/207467842-d92416da-c312-4a9c-9cbf-a23a93da6465.png
    favicon: https://raw.githubusercontent.com/healthinnovation/innovar/gh-pages/favicon.ico
    orientation: columns
    vertical_layout: fill
    navbar:
        - { icon: "fa-github", href: "https://github.com/healthinnovation", align: right}
        - { icon: "fa-home", href: "https://healthinnovation.github.io/Harmonize-Project/", align: left, title: "Return home"}
    
    self_contained: false
    lib_dir: "lib"
---


<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto+Slab&display=swap');
body{
    font-family: 'Roboto Slab', serif;
}

.navbar{
    padding-left: 28px;
}

.navbar-logo {
    margin-top: 2px;
    width: 36.5px;
    position: fixed;
    left: 2px;
    margin-bottom: 2px;
}

.navbar-inverse {
    background-color: #070807;
    border-color: #070807;
}
.navbar-inverse .navbar-brand {
    color: #ffffff;
}
.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
    color: #ffffff;
    background-color: #ffffff2e;
}
.navbar-inverse .navbar-nav>li>a {
    color: #ffffff;
}
.navbar-inverse .navbar-brand:hover, .navbar-inverse .navbar-brand:focus {
    color: #ffffff;
    background-color: #ffffff00;
}
</style>


```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(ggplot2)
library(tidyr)
library(plotly)
library(echarts4r)
```

```{r}
metadata <- readxl::read_excel(
  "data/metadata-20230129.xlsx"
  # , col_types = readr::cols(.default = "c"),
  # locale = readr::locale(encoding = "Latin1")
)
```

Main {data-icon="fa fa-bar-chart"}
=====================================================================


Column {data-width=650}
-----------------------------------------------------------------------

### Reviewed datasets by dimension

```{r}
reviewed_datasets <- metadata %>% 
  group_by(dimension) %>% 
  summarise(datasets = n(), .groups = "drop")
```

```{r}
reviewed_datasets_plot <- reviewed_datasets %>% 
  ggplot(aes(dimension, datasets, color = dimension, fill = dimension)) + 
  geom_bar(stat = "identity") + 
  scale_y_continuous(breaks = seq(0, max(reviewed_datasets$datasets), 5)) +
  scale_color_manual(values = c("#E64B35FF", "#4DBBD5FF", "#00A087FF")) +
  scale_fill_manual(values = c("#E64B35FF", "#4DBBD5FF", "#00A087FF")) +
  coord_flip() +
  guides(color = "none", fill = "none") +
  theme_minimal() + 
  labs(y = "Total reviewed datasets", x = "Dimension")
```

```{r}
reviewed_datasets_plot %>% 
  ggplotly() %>% 
  config(displayModeBar = F)
```

### Reviewed datasets by dimension along weeks

```{r}
collections_week_raw <- metadata %>% 
  mutate(
    access_week = lubridate::floor_date(as.Date(access_date), unit = "week")
  ) %>% 
  group_by(dimension, access_week) %>% 
  summarise(datasets = n(), .groups = "drop")
```

```{r}
collections_week <- collections_week_raw %>% 
  group_by(dimension) %>% 
  complete(
    access_week = seq.Date(
      min(collections_week_raw$access_week), 
      max(collections_week_raw$access_week), 
      by = "week"
    )
  ) %>% 
  replace_na(list(datasets = 0)) %>% 
  ungroup()
```

```{r}
collections_week_total <- collections_week %>% 
  pivot_wider(
    id_cols = access_week, names_from = dimension, values_from = datasets
  ) %>% 
  mutate(Total = Health + Demographics + Climate) %>% 
  pivot_longer(-access_week, names_to = "dimension", values_to = "datasets")
```

```{r}
collections_week_plot <- collections_week_total %>% 
  ggplot(
    aes(
      access_week, datasets, group = dimension, color = dimension, 
      linetype = dimension
    )
  ) +
  geom_point() +
  geom_line() +
  scale_linetype_manual(values = c(rep("dashed", 3), "solid")) +
  scale_color_manual(values = c("#E64B35FF", "#4DBBD5FF", "#00A087FF", "#000000")) +
  theme_minimal() +
  labs(
    x = "Week", y = "Reviewed datasets", color = "Dimension", 
    linetype = "Dimension"
  )
```

```{r}
collections_week_plot %>%
  ggplotly() %>%
  config(displayModeBar = F)
```

Column {data-width=450}
-----------------------------------------------------------------------

### Data provider map

```{r}
owners_edges <- readxl::read_excel("data/owners-edges.xlsx")
owners_nodes <- readxl::read_excel("data/owners-nodes.xlsx")
```

```{r}
nodes <- owners_nodes %>% 
  mutate(
    value = rep(1, nrow(owners_nodes)),
    size = rep(20, nrow(owners_nodes)),
    symbol = rep("circle", nrow(owners_nodes)),
    stringsAsFactors = "FALSE"
  )

edges <- owners_edges %>% 
  mutate(
    value = rep(1, nrow(owners_edges)),
    size = rep(2, nrow(owners_edges)),
    stringsAsFactors = FALSE
  )
```


```{r fig.width=7}
e_charts() |>
  e_graph(
    zoom = 3, edgeSymbol = c("none", "arrow"), edgeSymbolSize = c(0, 1), 
    lineStyle = list(curveness = 0.2)
  ) |>
  e_graph_nodes(nodes, name = owner, value, size, symbol, category = dimension) |>
  e_graph_edges(edges, source = owner_1, target = owner_2, value, size) |>
  e_color(color = c("#E64B35FF", "#00A087FF", "#4DBBD5FF")) |>
  e_tooltip()
```


Health {data-icon="fa fa-database"}
===============================================================

```{r}
metadata %>% 
  filter(dimension == "Health") %>% 
  reactable::reactable(highlight = TRUE)
```

Demographics {data-icon="fa fa-database"}
===============================================================

```{r}
metadata %>% 
  filter(dimension == "Demographics") %>% 
  reactable::reactable(highlight = TRUE)
```


Climate {data-icon="fa fa-database"}
===============================================================

```{r}
metadata %>% 
  filter(dimension == "Climate") %>% 
  reactable::reactable(highlight = TRUE)
```

